Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-21 cordillera-cycle.tex
Rev. Jarosch: add results of sensitivity tests.

>>>>

      Using the GRIP ice core palaeo-temperature record as climate forcing
      time-series, the model shows a significant sensitivity to selected ice
      rheologic and basal sliding parameters (Fig.~\ref{fig:sens_ts};
      Table~\ref{tab:sens_extrema}) in terms of modelled ice extent, and
      even more so in terms of modelled ice volumes.

      As a direct result of the different scaling factors applied
      (Table~\ref{tab:sens_params}), the resulting simulations show very
      little difference in the modelled glaciated areas corresponding to
      maximum ice volumes during MIS~2, but also during MIS~4
      (Table~\ref{tab:sens_extrema}). However, such can not be said of the
      modelled glaciated area corresponding to minimum ice volume during
      MIS~3. In fact, the extent of the remnant ice cap which persists over
      the Skeena Mountains during this stage shows a significant sensitivity
      to ice rheology of 31\,\unit{\%}, and an even more important
      sensitivity to basal sliding parameters of 62\,\unit{\%}
      (Table~\ref{tab:sens_extrema}).

      The modelled sea-level relevant ice volumes show more variability than
      the modelled glaciated areas (Table~\ref{tab:sens_extrema},
      Fig.~\ref{fig:sens_ts}). As one could expect, softer ice and weaker
      till both result in a thinner ice sheet, while harder ice and stronger
      till result in a thicker ice sheet. For instance, peak ice volume
      during the MIS~2 (LGM) varies by 30\,\unit{\%} between the two
      parametrisations of ice rheology used, and by 21\,\unit{\%} between
      the two parametrisations of basal sliding used. The differences in
      sea-level relevant ice volume are greatest during the MIS~3
      (Table~\ref{tab:sens_extrema}, Fig.~\ref{fig:sens_ts}) where both the
      areal and thickness contributions add up.
